\vspace{-2.5em} Spatio-angular transfer functions for fluorescence microscopes\vspace{-1em}

### 2018-04-20 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Missing factor of two on Ebfp.
Early draft of polarized OTF notes.

Although we will not use the result immediately, we can write the electric field
in the back focal plane under the paraxial approximation. We expand Eq. \ref{eq:bfp}
in a Taylor series about $r_b=0$ and drop all second-order and higher terms to
find
\begin{align}
  \mb{\tilde{e}}^{(p)}_b(\rb{};\ro{}, \so{}) \propto \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}
  \begin{bmatrix}
    1 & 0 &-\frac{r_b}{f_o}\cos\phi_b\\
    0&1&-\frac{r_b}{f_o}\sin\phi_b\\
    0&0&0
  \end{bmatrix}
  \begin{bmatrix}
    \cos\varphi_o\sin\vartheta_o\\
    \sin\varphi_o\sin\vartheta_o\\
    \cos\vartheta_o
  \end{bmatrix}
\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).\label{eq:bfppara}
\end{align}
We will continue to use a superscript $(p)$ to mark terms that have used the
paraxial approximation.

@@

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 1.\textwidth]{../calculations/compare-ft/psfs.pdf}
   \caption{\textbf{Left:} Point spread functions and \textbf{Right:} optical
     transfer functions for a single-view fluorescence microscope with
     $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
     \textbf{Black:} $l=0, m=0$ spherical harmonic---an isotropic distribution
     of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$ spherical
     harmonic---negative fluorophores near the transverse plane, positive
     fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $z$-oriented
     dipole.}
   \label{fig:para}
\end{figure}

>>>>

Although we will not use the result immediately, we can write the electric field
in the back focal plane under the paraxial approximation. We expand Eq. \ref{eq:bfp}
in a Taylor series about $r_b=0$ and drop all second-order and higher terms to
find
\begin{align}
  \mb{\tilde{e}}^{(p)}_b(\rb{};\ro{}, \so{}) \propto \me^{-i(kn_o/f_o)\rb{}\cdot\ro{}}
  \begin{bmatrix}
    1 & 0 &-\frac{2r_b}{f_o}\cos\phi_b\\
    0&1&-\frac{2r_b}{f_o}\sin\phi_b\\
    0&0&0
  \end{bmatrix}
  \begin{bmatrix}
    \cos\varphi_o\sin\vartheta_o\\
    \sin\varphi_o\sin\vartheta_o\\
    \cos\vartheta_o
  \end{bmatrix}
\Pi\left(\frac{r_b}{r_b^{\text{max}}}\right).\label{eq:bfppara}
\end{align}
We will continue to use a superscript $(p)$ to mark terms that have used the
paraxial approximation.

@@

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 1.\textwidth]{../calculations/compare-ft/psfs.pdf}
   \caption{\textbf{Left:} Point spread functions and \textbf{Right:} optical
     transfer functions for a single-view fluorescence microscope with
     $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
     \textbf{Black:} $l=0, m=0$ spherical harmonic term---an isotropic
     distribution of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$
     spherical harmonic term---negative fluorophores near the transverse plane,
     positive fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $z$-oriented
     dipole.}
   \label{fig:para}
\end{figure}
